Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2024-10-21 reviews.Rmd

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
manuscript-src : manuscript.Rmd
---

@@

We are sure this would be possible and enlightening, but also way beyond the scope of the current paper.
Out goal is more modest: we want to provide a bayesian justification of pre-registration that 1. clearly articulates the aims of a preregistration and 2. describes how preregistration achieves these goals.
As a result, it eliminates common missconceptions about preregistrations, for example, that you are not allowed to deviate under any circumstances.
To achieve these goals, our examples are purposely schematic, as we want them to apply to all empirical sciences.

>>>>

---
title          : "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
authors        : "Aaron Peikert, Maximilian S. Ernst & Andreas M. Brandmaier"
journal        : "Meta-Psychology"
manuscript-id  : "4139"
cutout-quotes  : true
class          : "draft"
output         : papaja::revision_letter_pdf
manuscript-src : manuscript.Rmd
bibliography   : references.bib
---

@@

We are sure this would be possible and enlightening, but also way beyond the scope of the current paper.
Out goal is more modest: we want to provide a Bayesian justification of pre-registration that 1. clearly articulates the aims of a preregistration and 2. describes how preregistration achieves these goals.
As a result, it eliminates common missconceptions about preregistrations, for example, that you are not allowed to deviate under any circumstances.
To achieve these goals, our examples are purposely schematic, as we want them to apply to all empirical sciences.
